### 2016-02-14 README.Rmd
typos
misc

The name `visdat` was chosen as I think in the future it could be integrated with R packages `testdat` and `testthat`. The idea being that first you visualise your data (`visdat`), then you run tests from `testdat` or `testthat` to fix them.

>>>>

The name `visdat` was chosen as I think in the future it could be integrated with [`testdat`](https://github.com/ropensci/testdat). The idea being that first you visualise your data (`visdat`), then you run tests from `testdat` to fix them.
